Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-22 edubots_surveys.Rnw
Make it compile again
Adds small text and figures for RQ2 refs #15

\def\includegraphic{}
\def\includegraphics{}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? }
\item{ RQ2 - Which kind of chatbots are they interested in? }
\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender,  or years of experience in Education? }
\item{ RQ4 - } 
\end{itemize}

@@

>>>>

%\def\includegraphic{}
%\def\includegraphics{}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}
\author[
  addressref={aff3},
  email={n.h.abbas@leeds.ac.uk}
]{\inits{N.}\fnm{Noorhan} \snm{Abbas}}

@@

\address[id=aff3]{%
  \orgdiv{School of Computing},
  \orgname{University of Leeds},          % university, etc
  \city{Leeds},                              % city
  \cny{UK}                                    % country
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Maybe move it to a different place later
As a starting point, we have analyzed the responses to a survey from XXX teachers asking about their attitudes towards the use of chatbots in their classes. We are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? }
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender, or years of experience in Education? }
\item{ RQ4 - } 
\end{itemize}

@@

\subsection{RQ2 - Which kind of chatbots would teachers find useful in their classes?}

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
    \end{minipage}
\end{center}
    \caption{Types of chatbots.}
\label{figure:chatbots_types}
\end{figure}
